An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-29 VLDB2026/main.tex
Update main.tex

	\textcolor{violet}{The first seven datasets are widely used in existing literature. As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}

	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}

>>>>

	\textcolor{violet}{The first seven datasets are widely used in existing works. As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}

	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes. For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
